Realizing temporal graphs from fastest travel times

### 2023-02-09 ICALP23-RealizingTemporalGraphs.tex
Submission

@@

\vspace{0,2cm}
\noindent \textbf{Due to lack of space, the full paper with all proofs is attached in a 
	clearly marked Appendix to be read at the discretion of the Program Committee.}
\end{abstract}

@@

Formally, let $G=(V,E)$ and $\Delta\in \mathbb{N}$, and let $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}$ be an edge-labeling function that assigns to every edge of $G$ exactly one of the labels from $\{1,\ldots,\Delta\}$. 
Then we denote by $(G,\lambda,\Delta)$ the \emph{$\Delta$-periodic temporal graph} $(G,L)$, where for every edge $e\in E$ we have $L(e)=\{i\Delta + x : i\geq 0, x\in \lambda(e)\}$. 
In this case we call $\lambda$ a \emph{$\Delta$-periodic labeling} of $G$. 
When it is clear from the context, we drop $\Delta$ form the notation and say that $(G,\lambda)$ is a ($\Delta$-periodic) temporal graph.
Given a duration matrix $D$, it is easy to observe that similar to the static case, if $D_{i,j}=1$, then $v_i$ and $v_j$ must be connected by an edge. We call the graph defined by those edges as the \emph{underlying graph} of $D$.

@@

We complement this result by showing that the problem is fixed-parameter tractable (FPT) with respect to the feedback edge number of the underlying graph (\cref{thm:FPTwrtFES}). 
Our FPT algorithm preprocesses the input graph in a suitable way that allows us to efficiently guess desired structures. Then we create integer linear programs (ILPs) (with bounded number of variables) and add constraints to those instances by suitably partitioning the fastest paths among pairs of vertices belonging to a small number of interesting sets. The notion of segment is crucial for adding the necessary and sufficient number of linear constraints. We use Lenstra's Theorem~\cite{Lenstra1983Integer} to solve the ILPs efficiently.

Note that this provides a fairly complete picture of the parameterized computational complexity of \deltaExact\ with respect to structural parameters of the underlying graph that measure ``tree-likeness''. To obtain our results, we prove several properties of fastest temporal paths, which may be of independent interest.

@@

To the best of our knowledge, we are the first to consider graph realization problems in the temporal setting. However, many other connectivity-related problems have been studied in the temporal setting~\cite{enright2021deleting,MolterRZ21,klobas2023interference,deligkas2022optimizing,erlebach2021temporal,Flu+19a,Zsc+19,CasteigtsCS22}, most of which are much more complex and computationally harder than their non-temporal counterparts, and some of which do not even have a non-temporal counterpart.

@@

Let $v_1,v_2,\ldots,v_n$ be the $n$ vertices of the graph $G$. 
For simplicity of the presentation~--and with a slight abuse of notation--~we refer during the paper to the entry $D_{i,j}$ of the matrix $D$ as 
$D_{a,b}$, where $a=v_i$ and $b=v_j$. That is, we put as indices of the matrix $D$ the corresponding vertices of $G$ whenever it is clear from the context.
Many times we also refer to a path $P=(u=v_1, v_2, \dots, v_p=v)$ from $u$ to $v$ in $G$,
as a temporal path in $(G,\lambda)$,
where we actually mean that $(P,\lambda,\Delta)$ is a temporal path with $P$ as its underlying (static) path.
We denote with $d(u,v,P)$ the duration of the fastest temporal path from $u$ to $v$ along path $P$. Note that $d(u,v,P) \geq d(u,v)$.

@@

\end{tikzpicture}
}
\caption{Illustration of the temporal graph $(G,\lambda)$ from the NP-hardness reduction, 
	where the NAE 3-SAT formula $\phi$ is of form $\phi = \text{NAE}(x_1, \overline{x}_2, x_3) \wedge \text{NAE}(\overline{x}_1, x_2, x_4)$.
To improve the readability, we draw edges between vertices $x_i^T$ and $x_j^F$ (where $i \neq j$) with gray dotted lines.
Presented is the labeling of $G$ corresponding to the assignment $x_1=x_2=\textsc{true}$ and $x_3,x_4=\textsc{false}$,
where all unlabeled edges get the label $2$.
}\label{fig:NP-example}
\end{figure}
%
We set $\Delta$ to some constant larger than two, that is, $\Delta\ge 3$. Next, we specify the durations in the matrix $D$ between all vertex pairs.
For the sake of simplicity we write $D_{u,v}$ as $d(u,v)$,
where $u,v$ are two vertices of $G$. 
We start by setting the value of $d(u,v) = 1$ where $u$ and $v$ are two adjacent vertices in $G$.
\begin{itemize}
    %\item For each variable $x$ in $\phi$ we specify the following distances between the non-adjacent variable vertices:
    %$d(x_1,x_2)=2$. 
    %\item For pair of variable $x,y$ in $\phi$ with $x\neq y$ we specify the following 
    %$d(x_1,y^T)=d(x_1,y^F)=3$, $d(x_2,y^T)=d(x_2,y^F)=2$.
    \item For each variable $x_i$ in $\phi$ and the super vertex $v$
    we specify the following durations:
    $d(x_i,v)=2$ and $d(v,x_i)= \Delta $. %, $d(x_2,v)=3$.
    \item For each clause $c$ in $\phi$ and the super vertex $v$
    we specify the following durations:
    $d(c,v)=2$ and $d(v,c)= \Delta - 1$.
    \item Let $x_i$ be a variable that appears in clause $c$, then  we specify the following durations:
    $d(c,x_i)=2$ and $d(x_i,c)=\Delta$.
    If $x_i$ appears non-negated in $c$ we specify the following durations:
    $d(c,x_i^F)=2$ and $d(x_i^F,c)=\Delta$.
    If $x_i$ appears negated in $c$ we specify the following duratios:
    $d(c,x_i^T)=2$ and $d(x_i^T,c)=\Delta$.
    \item Let $x_i$ be a variable that does \emph{not} appear in clause $c$, then we specify the following duratios:
    $d(x_i,c)=\Delta$, $d(c,x_i)=2\Delta + 2$
    and
    $d(c,x_i^T)=d(c,x_i^F)=2$, $d(x_i^T,c)=d(x_i^F,c)=\Delta$. 
    \item For each pair of variables $x_i \neq x_j$ in $\phi$ we specify the following duratios:
    $d(x_i,x_j)=2\Delta +1$ and
    $d(x_i,x_j^T)=d(x_i,x_j^F)=\Delta + 1$.
    \item For each pair of clauses $c_i \neq c_j$ in $\phi$ we specify the following duratios:
    $d(c_i,c_j)= \Delta + 1$.
\end{itemize}
This finishes the construction of the instance $(D,\Delta)$ of \deltaExact\, which can clearly be done in polynomial time. In the remainder we show that $(D,\Delta)$ is a \textsc{yes}-instance of \deltaExact\ if and only if NAE 3-SAT formula $\phi$ is satisfiable.

$(\Rightarrow)$: Assume the constructed instance $(D,\Delta)$ of \deltaExact\ is a \textsc{yes}-instance. 
Then there exist a label $\lambda(e)$ for each edge $e\in E(G)$ such that for each vertex pair $u,w$ in the temporal graph $(G,\lambda,\Delta)$ we have that a fastest temporal path from $u$ to $w$ is of duration $d(u,w)$. 
%In particular, for any two vertices $u,w$ with $d(u,w)=\infty$ we have that there does not exist a temporal path from $u$ to $w$ in $(G,\lambda)$.

@@

    \subparagraph{Connector gadget.} Next, we describe \emph{connector gadgets}. Intuitively, these gadgets will be used to connect many vertex pairs by fast paths, which will make arguing about possible labelings in \textsc{yes}-instances much easier. Connector gadgets consist of six vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$. 
    %Each connector gadget is associated with four sets $A,A',B,B'$ containing vertices of other gadgets. 
    Each connector gadget is associated with two sets $A,B$ with $B\subseteq A$ containing vertices of other gadgets. 
    Let $V^\star$ denote the set of all vertices from all edge selection gadgets and all validation gadgets.
    The sets $A$ and $B$ will only play a role when defining the matrix $D$ later. Informally speaking, vertices in $A$ should reach all vertices in $V^\star$ quickly through the gadget, except the ones in $B$.
    We have the following edges. 
    \begin{itemize}
        \item Edges $\{\hat{v}_0,\hat{v}_1\},\{\hat{v}_0',\hat{v}_1\},\{\hat{v}_1,\hat{v}_2\},\{\hat{v}_2,\hat{v}_3\},\{\hat{v}_2,\hat{v}_3'\}$.
        \item An edge between $\hat{v}_1$ and each vertex in $V^\star$.
        \item An edge between $\hat{v}_2$ and each vertex in $V^\star$.
    \end{itemize}
    We add two connector gadgets for each edge selection gadget and two connector gadgets for each validation gadget.

@@

In the remainder we prove that $D$ is a \textsc{yes}-instance of \deltaExactLong\ if and only if the $H$ is a \textsc{yes}-instance of \textsc{Multicolored Clique}.

\subparagraph{$(\Rightarrow)$:} Assume $D$ is a \textsc{yes}-instance of \deltaExactLong\ and let $(G,\lambda)$ be a solution. We have that the underlying graph $G$ is uniquely defined by $D$. We first prove a number of properties of $\lambda$ that we need to define a set of vertices in $H$ which we claim to be a multicolored clique.

@@

\subparagraph{$(\Leftarrow)$:} Assume $H$ is a \textsc{yes}-instance of \textsc{Multicolored Clique} and let $X$ be a solution. We construct the following labeling for the underlying graph $G$, see also \cref{fig:hardness1} for an illustration.

@@

Lastly, consider two vertices $v,v'\in V$. Note that before the addition of the infinity gadget, by construction of $G$ we have that $d(v,v')\le n^9+2$ or $d(v,v')=\infty$. Furthermore, if $D$ is a yes-instance, we have shown in the correctness proof of the reduction that the difference between the smallest label and the largest label is at most $n^9+1$. This implies that for a vertex pair $v,v'\in V$ with $d(v,v')=\infty$ we have in the periodic case with $\Delta=n^{11}$, that $d(v,v')\ge n^{11}-n^9>n^{10}$. Which means, after adding the vertices and edges of the infinity gadget, we indeed have that $d(v,v')=n^{10}$. For all vertex pairs $v,v'$ where in the original construction we have $d(v,v')\neq\infty$, we can also see that adding the infinity gadget and setting $\Delta=n^{11}$ does not change the duration of a fastest path from $v$ to $v'$, since all newly added temporal paths have duration at least $n^{10}$. We can conclude that the originally constructed instance $D$ is a yes-instance if and only if it remains a yes-instance after adding the infinity gadget and setting $\Delta=n^{11}$.
\end{proof}

@@

To overcome the above mentioned difficulties, we propose the following high-level strategy.
\begin{itemize}
    \item We identify a small number of ``interesting vertices'' between which we guess representative fastest paths.
    \item We show that we can determine most labels along each path up to an additive constant. We show that the number of labels we cannot determine along such a path is small. 
    \item For each additive constant and each non-determined label along such a path we introduce a variable for an integer linear program (ILP). 
    \item We use constraints in the ILP to ensure that alternative connections (not using the guessed fastest path) between vertex pairs are not too fast.
    \item We compute a solution to the ILP and construct a labeling from that solution. Since the ILP has few variables and not too many constraints, this computation can be done efficiently using Lenstra's Theorem~\cite{Lenstra1983Integer}.
\end{itemize}

@@

%%%%% HM: the two sentences below seem trivial to me.
%Note that we can easily solve \deltaExact\ by guessing the structure of temporal paths among all pairs of vertices.
%But, this would create $f(n,m)$ guesses (where $f(n,m)$ is an exponential function in $|V|=n$ and $|E| = m$), and the running time of the algorithm would be too big.
We approach the problem using some special properties, which allow us to create $f(k)$ different guesses for certain fastest temporal paths (where $f$ will be a double exponential function in the feedback edge number $k$).
We solve each guess by creating an ILP instance with $O(k^3)$ variables and $O(n^c)$ constraints, for some $c \in \mathbb{N}$.
If the ILP instance is a \textsc{yes}-instance then we will show that also $D$ is a \textsc{yes}-instance of \deltaExact.
Moreover, from a positive solution of the ILP instance we then construct the desired labeling $\lambda$.
If all constructed ILP instances are \textsc{no}-instances, then we will show that $D$ is a \textsc{no}-instance of \deltaExact.
Due to Lenstra's Theorem~\cite{Lenstra1983Integer} we know that an ILP instance can be solved in FPT time with respect to the number of variables.
Therefore, we can solve each of our ILP instances in FPT time with respect to $k$.
\end{comment}
%

>>>>

%%% APPENDIX
\usepackage{fancyhdr}
\setlength{\headheight}{30pt}
\pagestyle{fancyplain} { % define first page header and footer
% \fancyhead[L]{Course Report}
\fancyhead[C]{\textbf{APPENDIX}}
% \fancyhead[R]{\thepage of \pageref{LastPage}}
% \fancyfoot[L]{Jinho Hwang}
% \fancyfoot[C]{GWU}
% \fancyfoot[R]{CS}
}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt} % remove header lines and reset formats
\renewcommand{\footrulewidth}{0pt} % remove footer lines and reset formats

% define the rest of pages header and footer
% \fancyhead[L]{Course Report}
\fancyhead[OC]{\huge \textbf{APPENDIX}}
\fancyhead[EC]{\huge \textbf{APPENDIX}}
% \fancyhead[R]{\thepage of \pageref{LastPage}}
% \fancyfoot[L]{Jinho Hwang}
\fancyfoot[OC]{\thepage}
\fancyfoot[EC]{\thepage}
% \fancyfoot[R]{CS}

@@

%\vspace{0,2cm}
%\noindent \textbf{Due to lack of space, the full paper with all proofs is attached in a 
%	clearly marked Appendix to be read at the discretion of the Program Committee.}
\end{abstract}

@@

Formally, let $G=(V,E)$ and $\Delta\in \mathbb{N}$, and let $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}$ be an edge-labeling function that assigns to every edge of $G$ exactly one of the labels from $\{1,\ldots,\Delta\}$. 
Then we denote by $(G,\lambda,\Delta)$ the \emph{$\Delta$-periodic temporal graph} $(G,L)$, where for every edge $e\in E$ we have $L(e)=\{i\Delta + x : i\geq 0, x\in \lambda(e)\}$. 
In this case we call $\lambda$ a \emph{$\Delta$-periodic labeling} of $G$. 
When it is clear from the context, we drop $\Delta$ form the notation and 
we denote the ($\Delta$-periodic) temporal graph by $(G,\lambda)$.
Given a duration matrix $D$, it is easy to observe that similar to the static case, if $D_{i,j}=1$, then $v_i$ and $v_j$ must be connected by an edge. We call the graph defined by those edges as the \emph{underlying graph} of $D$.

@@

We complement this result by showing that the problem is fixed-parameter tractable (FPT) with respect to the feedback edge number $k$ of the underlying graph (\cref{thm:FPTwrtFES}). 
Our FPT algorithm works as follows on a high level. 
First we distinguish $O(k)$ vertices which we call ``interesting vertices''. 
Then, we guess the fastest temporal paths for each pair of these interesting vertices; as we prove, the number of choices we have for all these guesses is upper bounded by a function of $k$. 
Then we also make several further guesses (again using a bounded number of choices), which altogether leads us to specify a small (i.e.~bounded by a function of $k$) number of different configurations for the fastest paths between \emph{all pairs} of vertices. For each of these configurations, we must then make sure that the labels of our solution will not allow any other temporal path from a vertex $v_i$ to a vertex $v_j$ have a \emph{strictly smaller} duration than $D_{i,j}$.
This naturally leads us to build one Integer Linear Program (ILP) for each of these configurations. We manage to formulate all these ILPs by having a number of variables that is upper-bounded by a function of $k$. Finally we use Lenstra's Theorem~\cite{Lenstra1983Integer} to solve each of these ILPs in FPT time. At the end, our initial instance is a \textsc{Yes}-instance if and only if at least one of these ILPs is feasible.

The above results provide a fairly complete picture of the parameterized computational complexity of \deltaExact\ with respect to structural parameters of the underlying graph which measure ``tree-likeness''. To obtain our results, we prove several properties of fastest temporal paths, which may be of independent interest.

@@

To the best of our knowledge, we are the first to consider graph realization problems in the temporal setting. However, many other connectivity-related problems have been studied in the temporal setting~\cite{Mertzios-transitivity21,Akrida-explorer-21,enright2021deleting,MolterRZ21,klobas2023interference,deligkas2022optimizing,erlebach2021temporal,Flu+19a,Zsc+19,CasteigtsCS22,FuchsleMNR22}, most of which are much more complex and computationally harder than their non-temporal counterparts, and some of which do not even have a non-temporal counterpart.

@@

Let $v_1,v_2,\ldots,v_n$ be the $n$ vertices of the graph $G$. 
For simplicity of the presentation~--and with a slight abuse of notation--~we refer during the paper to the entry $D_{i,j}$ of the matrix $D$ as 
$D_{a,b}$, where $a=v_i$ and $b=v_j$. That is, we put as indices of the matrix $D$ the corresponding vertices of $G$ whenever it is clear from the context.
Many times we also refer to a path $P=(u=v_1, v_2, \dots, v_p=v)$ from $u$ to $v$ in $G$,
as a temporal path in $(G,\lambda,\Delta)$,
where we actually mean that $(P,\lambda,\Delta)$ is a temporal path with $P$ as its underlying (static) path.
We denote with $d(u,v,P)$ the duration of the fastest temporal path from $u$ to $v$ along path $P$. Note that $d(u,v,P) \geq d(u,v)$.

@@

\end{tikzpicture}
}
\caption{Illustration of the temporal graph $(G,\lambda)$ from the NP-hardness reduction, 
	where the NAE 3-SAT formula $\phi$ is of form $\phi = \text{NAE}(x_1, \overline{x}_2, x_3) \wedge \text{NAE}(\overline{x}_1, x_2, x_4)$.
To improve the readability, we draw edges between vertices $x_i^T$ and $x_j^F$ (where $i \neq j$) with gray dotted lines.
Presented is the labeling of $G$ corresponding to the assignment $x_1=x_2=\textsc{true}$ and $x_3,x_4=\textsc{false}$,
where all unlabeled edges get the label $2$.
}\label{fig:NP-example}
\end{figure}
%
We set $\Delta$ to some constant larger than two, that is, $\Delta\ge 3$. Next, we specify the durations in the matrix $D$ between all vertex pairs.
For the sake of simplicity we write $D_{u,v}$ as $d(u,v)$,
where $u,v$ are two vertices of $G$. 
We start by setting the value of $d(u,v) = 1$ where $u$ and $v$ are two adjacent vertices in $G$.
\begin{itemize}
    %\item For each variable $x$ in $\phi$ we specify the following distances between the non-adjacent variable vertices:
    %$d(x_1,x_2)=2$. 
    %\item For pair of variable $x,y$ in $\phi$ with $x\neq y$ we specify the following 
    %$d(x_1,y^T)=d(x_1,y^F)=3$, $d(x_2,y^T)=d(x_2,y^F)=2$.
    \item For each variable $x_i$ in $\phi$ and the super vertex $v$
    we specify the following durations:
    $d(x_i,v)=2$ and $d(v,x_i)= \Delta $. %, $d(x_2,v)=3$.
    \item For each clause $c$ in $\phi$ and the super vertex $v$
    we specify the following durations:
    $d(c,v)=2$ and $d(v,c)= \Delta - 1$.
    \item Let $x_i$ be a variable that appears in clause $c$, then  we specify the following durations:
    $d(c,x_i)=2$ and $d(x_i,c)=\Delta$.
    If $x_i$ appears non-negated in $c$ we specify the following durations:
    $d(c,x_i^F)=2$ and $d(x_i^F,c)=\Delta$.
    If $x_i$ appears negated in $c$ we specify the following duratios:
    $d(c,x_i^T)=2$ and $d(x_i^T,c)=\Delta$.
    \item Let $x_i$ be a variable that does \emph{not} appear in clause $c$, then we specify the following duratios:
    $d(x_i,c)=\Delta$, $d(c,x_i)=2\Delta + 2$
    and
    $d(c,x_i^T)=d(c,x_i^F)=2$, $d(x_i^T,c)=d(x_i^F,c)=\Delta$. 
    \item For each pair of variables $x_i \neq x_j$ in $\phi$ we specify the following duratios:
    $d(x_i,x_j)=2\Delta +1$ and
    $d(x_i,x_j^T)=d(x_i,x_j^F)=\Delta + 1$.
    \item For each pair of clauses $c_i \neq c_j$ in $\phi$ we specify the following duratios:
    $d(c_i,c_j)= \Delta + 1$.
\end{itemize}
This finishes the construction of the instance $(D,\Delta)$ of \deltaExact\, which can clearly be done in polynomial time. In the remainder we show that $(D,\Delta)$ is a \textsc{Yes}-instance of \deltaExact\ if and only if NAE 3-SAT formula $\phi$ is satisfiable.

$(\Rightarrow)$: Assume the constructed instance $(D,\Delta)$ of \deltaExact\ is a \textsc{Yes}-instance. 
Then there exist a label $\lambda(e)$ for each edge $e\in E(G)$ such that for each vertex pair $u,w$ in the temporal graph $(G,\lambda,\Delta)$ we have that a fastest temporal path from $u$ to $w$ is of duration $d(u,w)$. 
%In particular, for any two vertices $u,w$ with $d(u,w)=\infty$ we have that there does not exist a temporal path from $u$ to $w$ in $(G,\lambda)$.

@@

    \subparagraph{Connector gadget.} Next, we describe \emph{connector gadgets}. Intuitively, these gadgets will be used to connect many vertex pairs by fast paths, which will make arguing about possible labelings in \textsc{Yes}-instances much easier. Connector gadgets consist of six vertices $\hat{v}_0,\hat{v}_0',\hat{v}_1,\hat{v}_2,\hat{v}_3,\hat{v}_3'$. 
    %Each connector gadget is associated with four sets $A,A',B,B'$ containing vertices of other gadgets. 
    Each connector gadget is associated with two sets $A,B$ with $B\subseteq A$ containing vertices of other gadgets. 
    Let $V^\star$ denote the set of all vertices from all edge selection gadgets and all validation gadgets.
    The sets $A$ and $B$ will only play a role when defining the matrix $D$ later. Informally speaking, vertices in $A$ should reach all vertices in $V^\star$ quickly through the gadget, except the ones in $B$.
    We have the following edges. 
    \begin{itemize}
        \item Edges $\{\hat{v}_0,\hat{v}_1\},\{\hat{v}_0',\hat{v}_1\},\{\hat{v}_1,\hat{v}_2\},\{\hat{v}_2,\hat{v}_3\},\{\hat{v}_2,\hat{v}_3'\}$.
        \item An edge between $\hat{v}_1$ and each vertex in $V^\star$.
        \item An edge between $\hat{v}_2$ and each vertex in $V^\star$.
    \end{itemize}
    We add two connector gadgets for each edge selection gadget and two connector gadgets for each validation gadget.

@@

In the remainder we prove that $D$ is a \textsc{Yes}-instance of \deltaExactLong\ if and only if the $H$ is a \textsc{Yes}-instance of \textsc{Multicolored Clique}.

\subparagraph{$(\Rightarrow)$:} Assume $D$ is a \textsc{Yes}-instance of \deltaExactLong\ and let $(G,\lambda)$ be a solution. We have that the underlying graph $G$ is uniquely defined by $D$. We first prove a number of properties of $\lambda$ that we need to define a set of vertices in $H$ which we claim to be a multicolored clique.

@@

\subparagraph{$(\Leftarrow)$:} Assume $H$ is a \textsc{Yes}-instance of \textsc{Multicolored Clique} and let $X$ be a solution. We construct the following labeling for the underlying graph $G$, see also \cref{fig:hardness1} for an illustration.

@@

Lastly, consider two vertices $v,v'\in V$. Note that before the addition of the infinity gadget, by construction of $G$ we have that $d(v,v')\le n^9+2$ or $d(v,v')=\infty$. Furthermore, if $D$ is a \textsc{Yes}-instance, we have shown in the correctness proof of the reduction that the difference between the smallest label and the largest label is at most $n^9+1$. This implies that for a vertex pair $v,v'\in V$ with $d(v,v')=\infty$ we have in the periodic case with $\Delta=n^{11}$, that $d(v,v')\ge n^{11}-n^9>n^{10}$. Which means, after adding the vertices and edges of the infinity gadget, we indeed have that $d(v,v')=n^{10}$. For all vertex pairs $v,v'$ where in the original construction we have $d(v,v')\neq\infty$, we can also see that adding the infinity gadget and setting $\Delta=n^{11}$ does not change the duration of a fastest path from $v$ to $v'$, since all newly added temporal paths have duration at least $n^{10}$. We can conclude that the originally constructed instance $D$ is a \textsc{Yes}-instance if and only if it remains a \textsc{Yes}-instance after adding the infinity gadget and setting $\Delta=n^{11}$.
\end{proof}

@@

To overcome the above mentioned difficulties, we propose the following high-level strategy.
\begin{itemize}
    \item We identify a small number of ``interesting vertices'' between which we guess representative fastest paths.
    \item We show that we can determine most labels along each path up to an additive constant. We show that the number of labels we cannot determine along such a path is small. 
    \item For each additive constant and each non-determined label along such a path we introduce a variable for an Integer Linear Program (ILP). 
    \item We use constraints in the ILP to ensure that alternative connections (not using the guessed fastest path) between vertex pairs are not too fast.
    \item We compute a solution to the ILP and construct a labeling from that solution. Since the ILP has few variables and not too many constraints, this computation can be done efficiently using Lenstra's Theorem~\cite{Lenstra1983Integer}.
\end{itemize}

@@

%%%%% HM: the two sentences below seem trivial to me.
%Note that we can easily solve \deltaExact\ by guessing the structure of temporal paths among all pairs of vertices.
%But, this would create $f(n,m)$ guesses (where $f(n,m)$ is an exponential function in $|V|=n$ and $|E| = m$), and the running time of the algorithm would be too big.
We approach the problem using some special properties, which allow us to create $f(k)$ different guesses for certain fastest temporal paths (where $f$ will be a double exponential function in the feedback edge number $k$).
We solve each guess by creating an ILP instance with $O(k^3)$ variables and $O(n^c)$ constraints, for some $c \in \mathbb{N}$.
If the ILP instance is a \textsc{Yes}-instance then we will show that also $D$ is a \textsc{Yes}-instance of \deltaExact.
Moreover, from a positive solution of the ILP instance we then construct the desired labeling $\lambda$.
If all constructed ILP instances are \textsc{No}-instances, then we will show that $D$ is a \textsc{No}-instance of \deltaExact.
Due to Lenstra's Theorem~\cite{Lenstra1983Integer} we know that an ILP instance can be solved in FPT time with respect to the number of variables.
Therefore, we can solve each of our ILP instances in FPT time with respect to $k$.
\end{comment}
%
